Increasing quality of self-recovering images using BPCS Steganography

### 2014-11-05 Paper/main.tex
section 6 proof read
Added title page and plagiarism form
minor changes

\hspace{0pt} \\
As a solution to this problem each bit plane block used for embedding is treated as a separate embedding entity.
There is thus no overlap between two different blocks used for embedding.
The image reference content is first processed using the method explained later in this section.
Each block of the original image, which can store 192 bits, has 12 pixels (with a bit depth of 16 bits, in other words 192 bits) of the image reference content embedded into it.
An embedding map containing the location of the first pixel to be embedded in the block is also created to keep track of which pixels of the original image contains image reference content.
Since the individual image reference content pixels are embedded in order it is only necessary to know the location of the first pixel.
This embedding map is then embedded into the LSB (Least significant bit) layer of that specific 8x8 section of pixels. 
This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
This serves to give random access to the embedded content which is an essential property of self-embedding \cite{korus2013efficient}.
This is essential in order for the reconstruction process to function properly.

@@

\paragraph{Image resizing}
\label{ImageCompression}
The image reference content that is embedded into the original image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
The proposed method however does not utilize compression as it is beyond the scope of this dissertation.
The proposed method rather reduces the bit rate of the image from 24 bits to 16 which reduces the size of each pixel by 6 bits.
This means that the image size is reduced due to fewer bits being stored for each pixel.
The quality of the image is reduced using this method by reducing the amount of colours that a pixel can represent.
The image's size is also reduced according to the space available for embedding.
This is accomplished by calculating the amount of bits that can be embedded into in the original image.
The image is scaled down to the largest possible size that can still be embedded into the original image(determined by the calculated embedding capacity).
This means that the image reference content quality is at a maximum. 
When extracting the image reference content again the assembled image reference content is scaled up to it's original size of 512x512 pixels, which is the standard image size for the proposed method, before completing the reconstruction.
All image scaling was done by converting the image data to a Java image object, using the built in Java image scaling feature and then converting the resulting scaled image back to the required format.
This is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.

>>>>

\hspace{0pt} \\
As a solution to this problem each bit plane block used for embedding is treated as a separate embedding entity.
There is thus no overlap between two different blocks used for embedding.
The image reference content is first processed using the method explained later in this section.
Each block of the original image, which can store 192 bits, has 12 pixels (with a bit depth of 16 bits, in other words 192 bits) of the image reference content embedded into it.
An embedding map containing the location of the first pixel to be embedded in the block is also created to keep track of which pixels of the original image contains which pixels of the image reference content.
Since the individual image reference content pixels are embedded in order it is only necessary to know the location of the first pixel.
This embedding map is then embedded into the LSB (Least significant bit) layer of that specific 8x8 section of pixels. 
This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
This serves to give random access to the embedded content which is an essential property of self-embedding \cite{korus2013efficient}.
This is essential in order for the reconstruction process to function properly.

@@

\paragraph{Image resizing}
\label{ImageCompression}
The image reference content that is embedded into the original image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
The proposed method however does not utilize compression as it is beyond the scope of this dissertation.
The proposed method rather reduces the bit rate of the image from 24 bits to 16 which reduces the size of each pixel by 6 bits.
This means that the image size is reduced due to fewer bits being stored for each pixel.
The quality of the image is reduced using this method by reducing the amount of colours that a pixel can represent.
The image's size is also reduced according to the space available for embedding.
This is accomplished by calculating the amount of bits that can be embedded into in the original image.
The image is scaled down to the largest possible size that can still be embedded into the original image(determined by the calculated embedding capacity).
This means that the image reference content quality is at a maximum. 
When extracting the image reference content again the assembled image reference content is scaled up to it's original size of 512x512 pixels, which is the standard image size for the proposed method, before completing the reconstruction.
All image scaling was done by converting the image data to a Java image object, using the built in Java image scaling feature and then converting the resulting scaled image back to the required format.
This scaling up is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.
